Headgroup Structure and Cation Binding in Phosphatidylserine Lipid Bilayers

### 2019-09-11 Manuscript/manuscriptPS.tex
Experiments

The magnitudes of headgroup and glycerol backbone C--H bond order parameters of 1-palmitoyl-2-oleoyl-{\it sn}-glycero-3-phospho-L-serine (POPS)
were determined by measuring the chemical-shift resolved dipolar splittings
with a R-type Proton Detected Local Field (R-PDLF) experiment~\cite{dvinskikh04}.
The corresponding order parameter signs were measured with a S-DROSS experiment~\cite{gross97}
using natural abundance $^{13}$C solid state NMR spectroscopy as described previously \cite{ferreira13,ferreira16}.
The experiments were done in a Bruker Avance III 400 spectrometer operating at a $^1$H Larmor frequency of 400.03~MHz.
Magic angle spinning (MAS) of the sample was used at a frequency of 5.15~kHz (R-PDLF) and 5~kHz (S-DROSS).
The following experimental setups were used.

>>>>

The magnitudes of headgroup and glycerol backbone C--H bond order parameters of 1-palmitoyl-2-oleoyl-{\it sn}-glycero-3-phospho-L-serine (POPS)
were determined by measuring the chemical-shift-resolved dipolar splittings
with a R-type Proton Detected Local Field (R-PDLF) experiment~\cite{dvinskikh04}.
The corresponding order parameter signs were measured with a S-DROSS experiment~\cite{gross97}
using natural abundance $^{13}$C solid state NMR spectroscopy as described previously \cite{ferreira13,ferreira16}.
The experiments were done in a Bruker Avance III 400 spectrometer operating at a $^1$H Larmor frequency of 400.03~MHz.
Magic angle spinning (MAS) of the sample was used at a frequency of 5.15~kHz (R-PDLF) and 5~kHz (S-DROSS).
The following experimental setups were used.
